### 2019-12-15 README.Rmd
use updated code of conduct

Please note that this project is released with a 
[Contributor Code of Conduct](CONDUCT.md). By participating in this project you 
agree to abide by its terms.

>>>>

## Code of Conduct

Please note that the visdat project is released with a [Contributor Code of Conduct](http://visdat.njtierney.com/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
